He-Man: A domain-specific language for lightweight concurrency

### 2011-12-12 report/report.tex
Added front-end grammar, other work

%XXX: abstract

@@

Network applications need to support many simultaneous clients---this is known
as the C10K (``10,000 client'') problem\cite{Kegel}. Modern servers have enough
memory and bandwidth for massive concurrency, but it is difficult to design
applications to take full advantage of these resources.

@@

The Lighttpd\cite{Lighttpd} and Nginx\cite{Nginx} HTTP servers use event-based
architectures, with the stated goal of addressing the C10k problem. Indeed, they
are fast (XXX CITATION)

@@

\section{Front-end}

\section{Back-end}

@@

\begin{figure}[ht]
\centering
\bnf{
\i{Thread}
\p{(\i{thread\_label}, [(\i{Var}, \i{Type})])}
\i{Block}
\p{(\i{label}, \i{thread\_label}, [\i{Stmt}], \i{Tail})}
\i{Tail}
\p{\b{Goto} \i{label}}
\a{\b{GotoWait} \i{label}}
\a{\b{If} \i{Expr} \i{Tail} \i{Tail}}
\a{\b{Exit}}
\i{Stmt}
\p{\b{Decl} (\i{Var}, \i{Type}) \i{Expr}}
\a{\b{Assign} \i{Expr} \i{Expr}}
\a{\b{Exp} \i{Expr}}
\a{\b{Spawn} \i{label} [((\i{Var}, \i{Type}), \i{Expr})]}
}
\caption{Back-end grammar}
\end{figure}

@@

@@

@@

\bibliography{citations}{}
\bibliographystyle{plain}

>>>>

\begin{abstract}
TODO
\end{abstract}

@@

Network applications need to support many simultaneous clients---this is known
as the C10K (``10,000 client'') problem \cite{Kegel}. Modern servers have enough
memory and bandwidth for massive concurrency, but it is difficult to design
applications to take full advantage of these resources.

@@

The Lighttpd \cite{Lighttpd} and Nginx \cite{Nginx} HTTP servers use event-based
architectures, with the stated goal of addressing the C10k problem. Indeed, they
are fast (XXX CITATION)

@@

\section{The event loop model}

Event loops are a good way to get the level of concurrency that you need

we don't need arbitrary interleaving of instructions,

there shouldn't be much

and I/O time (both network and disk) probably dominates computation time

thus it's important to run short computations until a thread blocks,

@@

\section{Implementation}

\subsection{Front-end}

\begin{figure}[ht]
\centering
\bnf{
\i{Stmt}
\p{\b{Decl} (\i{Var}, \i{Type}) \i{Expr}}
\a{\b{While} \i{Expr} [\i{Stmt}]}
\a{\b{If} \i{Expr} [\i{Stmt}] [\i{Stmt}]}
\a{\b{Spawn} ([(\i{Var}, \i{Type})], [\i{Stmt}]) [\i{Expr}]}
\a{\b{Assign} \i{Expr} \i{Expr}}
\a{\b{Exp} \i{Expr}}
\a{\b{Wait} \i{Expr}}
\a{\b{Exit}}
\i{Expr}
\p{\b{Call} \i{String} [\i{Expr}]}
\a{\b{Arith} \i{ArithOp} \i{Expr} \i{Expr}}
\a{\b{ArithUnop} \i{ArithUnop} \i{Expr}}
\a{\b{RelnOp} \i{RelnOp} \i{Expr} \i{Expr}}
\a{\b{Constant} \i{String}}
\a{\b{NumLit} \i{Integer}}
\a{\b{StringLit} \i{String}}
\a{\b{Var} \i{String}}
\a{\b{CurThread}}
\i{Type} 
\p{\b{Int} $\mid$ \b{Bool} $\mid$ \b{String}
   $\mid$ \b{FD} $\mid$ \b{Buffer} $\mid$ \b{Event}}
}
\caption{Front-end grammar.}
\end{figure}

\subsection{Back-end}

\begin{figure}[ht]
\centering
\bnf{
\i{Thread}
\p{(\i{thread\_label}, [(\i{Var}, \i{Type})])}
\i{Block}
\p{(\i{label}, \i{thread\_label}, [\i{Stmt}], \i{Tail})}
\i{Tail}
\p{\b{Goto} \i{label}}
\a{\b{GotoWait} \i{label}}
\a{\b{If} \i{Expr} \i{Tail} \i{Tail}}
\a{\b{Exit}}
\i{Stmt}
\p{\b{Decl} (\i{Var}, \i{Type}) \i{Expr}}
\a{\b{Assign} \i{Expr} \i{Expr}}
\a{\b{Exp} \i{Expr}}
\a{\b{Spawn} \i{label} [((\i{Var}, \i{Type}), \i{Expr})]}
}
\caption{Back-end grammar.}
\end{figure}

\subsection{Runtime}

@@

less space per thread

decide when to allow internal if statements

@@

observable sharing (?)

@@

\bibliography{citations}{}
\bibliographystyle{abbrvnat}
